\section{September 30, 2022}
\subsection{Officer Meeting}

\subsubsection{Roll Call}
The following officers were present

\begin{enumerate}
    \item \president
    \item \tresurer
    \item \primaryprogrammer
    \item \secretary
\end{enumerate}

The following officers where not present or online

\begin{enumerate}
    \item \vicepresident (Pet Emergency)
\end{enumerate}

\subsubsection{Officers Updates}

\textbf{\president}

<<<<<<< Updated upstream
No Updates

\textbf{\vicepresident}

No Updates
=======
\begin{enumerate}
    \item Signed and forwared the eSAB Allotment form to Dr. Witty
    \item There's a CS club at Millard West High School in Omaha who reached out to us and is interested in hosting some sort of event or speaker. Is anyone free on Monday October 3 at 3:15 PM?
\end{enumerate}
>>>>>>> Stashed changes

\textbf{\vicepresident}

No Updates

\textbf{\tresurer}

\begin{itemize}
    \item eSAB have given us approximately \$150. 
    \item We can get the pokerchips.
    \item They cannot fund stickers. This will be out of pocket cost.
    \item Reduced the number of Arduino Uno \& Nano to 2.
    \item Reduced number of other hardware to 1.
    \item Check SOFS and we have: \$AMOUNT.
    \item Moved journal over to \href{https://github.com/OS2G/journal}{https://github.com/OS2G/journal}
\end{itemize}

\textbf{\primaryprogrammer}

No Updates

\textbf{\secretary}

No Updates

\subsubsection{Topic Discussed}

No other topics to discuss

\subsection{Actions}

\textbf{\primaryprogrammer}

\begin{enumerate}
    \item Fill out EPR for FOSS Jam.
\end{enumerate}

\textbf{\tresurer}

\begin{enumerate}
    \item Order Poker Chips
    \item Order Stickers
    \item Get Hardware
    \item Email Bauer
\end{enumerate}

\subsection{General Meeting}
\subsubsection{Number of Members} 

7 Total Members. 4 Officers.

\subsection{Topic Discussed}
Editor Wars