\section{December 13, 2022}

\subsection{Roll Call}

The following officers were present:

\begin{enumerate}
    \item \president
    \item \tresurer
    \item \primaryprogrammer
    \item \secretary
\end{enumerate}

No officers were absent
\\
Other members present:
\begin{enumerate}
    \item Mitch
    \item Timothy Gibbons
\end{enumerate}

\subsection{Standardized Officer Roles}
    \subsubsection{President}
        \begin{itemize}
            \item Help create meeting ideas
            \item Lead meetings
            \item Give content talks at meetings
        \end{itemize}
    \subsubsection{Treasurer}
        \begin{itemize}
            \item Keep track of club budget
        \end{itemize}
    \subsubsection{Primary Programmer}
        \begin{itemize}
            \item Room reservations
            \item EPRs
            \item Update calendar and website
        \end{itemize}
    \subsubsection{Secretary}
        \begin{itemize}
            \item Take meeting minutes
            \item Send out announcements
            \begin{itemize}
                \item Discord
                \item Google group email list
                \begin{itemize}
                    \item may encounter problems with non-school emails
                \end{itemize}
                \item Bits and Bytes
                \item Possibly NvolveU?
                \item We don't want to use too many platforms
            \end{itemize}
            
        \end{itemize}

\subsection{Recruitment}
Finding Consistent Members
    \begin{itemize}
        \item Build a good reputation
        \item Advertise to the target audience
    \end{itemize}
Finding Consistent \emph{Knowledgeable} Members
    \begin{itemize}
        \item Finding what these people want
        \item Long term this will help to give us knowledgeable officers as well
    \end{itemize}
CornHacks
    \begin{itemize}
        \item \href{https://unlcornhacks.com/#/home}{CornHacks Website}
        \item Hackathon over Feb. 4-5
        \item We could have a table of advisors
    \end{itemize}

\subsection{Hack Days}
Making Hack Days more engaging:
\begin{itemize}
    \item Making them similar to the "lab section" of a class
    \item Shadow the talks we have planned
\end{itemize}

\subsection{Meeting Location}
We may want to move the club to Avery Hall
\begin{itemize}
    \item Makes organizing meetings easier
    \item Gives members a reliable place to meet
    \item Right in the middle of the Computer Science Department
\end{itemize}
A room on the third floor may be best so that there are enough outlets

\subsection{Meeting Ideas}
\begin{itemize}
    \item Cluster Computing - Carl Lundstedt (HCC)
    \item Speaker from System76
    \begin{itemize}
        \item Mitch can connect us to them
        \item Make Linux laptops
        \item Made Pop-OS
    \end{itemize}
    \item Soup Night Social
    \item Mitch Lightning Talk
    \begin{itemize}
        \item Needs to be recorded
        \item Talk to Danial Schurr for OS2G specific slides
    \end{itemize}
    \item Embedded systems and prototyping crash course (Arduino?)
    \item "Meta" meeting about learning computer skills efficiently
    \begin{itemize}
        \item overview of topics and projects for members to work on
        \item would give new members somethign to latch on to
    \end{itemize}
    \item Lightning Talks?
    \begin{itemize}
        \item Mitch?
        \item Tim? (Game engine - contact GameDev club)
        \item Aaron?
        \item Luke?
        \item Dr. Bauer
        \item Dr. Balkir or a grad student working with him (RISC-V)
        \item Alex? (ScropTheOSAdvenduterer)
    \end{itemize}
\end{itemize}

\subsection{Long Term Goals}
Consolidate all the club's organizational material in one place:
\begin{itemize}
    \item Put it all on SharePoint
    \item Organize the resources on SharePoint
\end{itemize}
Putting valuable information on the club's GitHub and website 
\begin{itemize}
    \item can we convince general members to add these things?
\end{itemize}

\subsection{Tentative Meeting Schedule}
Jan 27 - Welcome back 
\begin{itemize}
    \item Probably just for returning members
\end{itemize}
Feb 3 - \underline{Talk}
\begin{itemize}
    \item Programming Languages
    \item Meta Programming Concepts
    \item Luke will reach out to Bourke
\end{itemize}
Feb 10 - \underline{Workshop}
\begin{itemize}
    \item Python?
    \item C
    \item Java Crash Course
\end{itemize}
Feb 17 - \underline{HackDay} (Soup Day)
Feb 24 - \underline{Talk} by Mitch
\begin{itemize}
    \item What's in a Name?
\end{itemize}
Mar 3 - \underline{Workshop}
\begin{itemize}
    \item TBD by Mitch
\end{itemize}
Mar 10 - \underline{HackDay}
\begin{itemize}
    \item LAN Party???
\end{itemize}
Mar 24 - \underline{Talk}
\begin{itemize}
    \item Embedded Systems?
    \item Arduino?
    \item Bauer
\end{itemize}
Mar 31 - \underline{Workshop} 
\begin{itemize}
    \item Embedded System Project
\end{itemize}
Apr 7 - \underline{HackDay} (Social)
Apr 14 - \underline{Talk}
\begin{itemize}
    \item Server Administration
    \item Erbey Reach out to Garhand
\end{itemize}
Apr 21 - \underline{Workshop} 
\begin{itemize}
    \item Server Administration
\end{itemize}
Apr 28 - \underline{HackDay} (Ice cream party)